---
title: "Details about the package"
author: "K. Masmoudi <khalil@via.ecp.fr>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Details about the package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# farsP quickstart guide

The goal of this document is to get you up and running with farsP as quickly as possible.
farsP is designed to read and summarize data from the "[US National Highway Traffic Safety Administration's Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS))".

Thi package functions may be tested "[this data](https://d3c33hcgiwev3.cloudfront.net/_e1adac2a5f05192dc8780f3944feec13_fars_data.zip?Expires=1505088000&Signature=MAhUuYxuAn89A7vbFOIuF~OQhfAodK60g4L23AHI2eFzw29oBgTsPc4prtS6XNivQDwrmNBtUo79ZGPrbvLuaPNhow0bAw8ArRC822Q-9CadF1hfO-zLYZlfm3qdJ0pfSDDqjvWgy5rx4v8hHdjvsMQXXMVp4mGqNcpHkxX7AYc_&Key-Pair-Id=APKAJLTNE6QMUY6HBC5A)".

The are two important functions in this package. The first function can be used to summarize the accidents' data by year and by month. The second produces a map graphic containing the accidents' locations.

## Summarizing accidents data : 

To summarize the data about accidents for a given set of years, one can use the function `fars_summarize_years`.  This function reads years and months from data for a given set of years and returns a tbl data frame containing the number of accidents summarized by year.
```{r eval=FALSE}
# Get summary for the year 2013
fars_summarize_years(2013)

# Get summary for multiple years (2013, 2014 and 2015)
fars_summarize_years(2013:2015)
```

## Producing map of accidents

A maps graphic containing the accidents' locations for a given year and given state can be produced using the function `fars_map_state`. This function function take as parameters the state specified as a numeric value and a set of year which is a numeric value to specify the year for which the graphic is plotted. A map plot of accidents location is returned.

```{r eval=FALSE}
# Plot the accidents map for the state number 1 during the year 2013
fars_map_state(1,2013)
```
